Hyperopt-Sklearn: Automatic Hyperparameter Configuration for Scikit-Learn

### 2014-05-24 papers/2014-automl/paper.tex
minor modifs from reviews

Taking a step back though, there is often no particular reason to use either an RBF-SVM or an RF when they are both computationally viable.
A model-agnostic practitioner may simply prefer to go with the one that provides greater accuracy.
In this light, {\em the choice of classifier can be seen as hyperparameter} alongside the $C$-value in the SVM and the max-tree-depth of the RF.
Indeed the choice and configuration of {\em pre-processing} components may likewise be seen as part of the model selection / hyperparameter optimization problem.
The Auto-Weka project \citep{thornton+hutter+hoos+leyton-brown:2012} was the first to show that an entire library of machine learning approaches (Weka~\citep{hall2009weka}) can be searched within the scope of a single run of hyperparameter tuning.
However, Weka is a GPL-licensed Java library, and was not written with scalability in mind. These factors limit the utility of Auto-Weka.
Scikit-learn~\citep{sklearn} is another library of machine learning algorithms that is written in Python with many modules in C for greater speed, and is BSD-licensed.
Scikit-learn is widely used in the scientific Python community and supports many machine learning application areas.

With this paper we introduce Hyperopt-Sklearn -- a project that brings the benefits of automatic algorithm configuration to users of Python and scikit-learn.
Hyperopt-Sklearn uses Hyperopt~\citep{hyperopt} to describe a search space over possible configurations of Scikit-Learn components, including pre-processing and classification modules.
Section 2 describes our configuration space of 7 classifiers and 4 preprocessing modules that encompasses a strong set of classification systems for dense and sparse feature classification (of images and text).
Section 3 presents experimental evidence that search over this space is viable, meaningful, and effective.
Section 4 presents a discussion of the results, and directions for future work.

@@

\begin{table}
  \begin{threeparttable}
    \caption{
        Hyperopt-sklearn scores relative to selections from literature on the three data sets used in our experiments.
        On MNIST, hyperopt-sklearn is one of the best-scoring methods that does not use image-specific domain knowledge (these scores and others may be found at http://yann.lecun.com/exdb/mnist/).
	On 20 Newsgroups, hyperopt-sklearn is competitive with similar approaches from the literature (scores taken from~\citet{guan2009class}).
        On Convex Shapes, hyperopt-sklearn outperforms previous automatic algorithm configuration approaches~\citep{eggensperger+etal:2013} and manual tuning~\citep{larochelle+etal:2007}.
    }
    \label{tbl:acc}
    \centering
    \small
    \begin{tabular}{llllll}
        \hline
        \multicolumn{2}{c}{\textbf{MNIST}} & \multicolumn{2}{c}{\textbf{20 Newsgroups}} & \multicolumn{2}{c}{\textbf{Convex Shapes}}  \\
        Approach & Accuracy  & Approach & F-Score & Approach & Accuracy\\
        \hline
	Committee of convnets & 99.8\%                & CFC & 0.928 & \textbf{hyperopt-sklearn} & \textbf{88.7}\%\\
	\textbf{hyperopt-sklearn} & \textbf{98.7}\%   & \textbf{hyperopt-sklearn} & \textbf{0.856} & hp-dbnet & 84.6\% \\
        libSVM grid search & 98.6\%                   & SVMTorch & 0.848 & dbn-3 & 81.4\%\\
        Boosted trees & 98.5\%                        & LibSVM & 0.843 &  &  \\
    \end{tabular}
    \begin{tablenotes}
      \footnotesize
      \item
	      \textit{In the 20 Newsgroups dataset, the score reported for hyperopt-sklearn is the weighted-average F1 score provided by sklearn. The other approaches shown here use the macro-average F1 score.} 
    \end{tablenotes}
  \end{threeparttable}
\end{table}

@@

>>>>

Taking a step back though, there is often no particular reason to use either an RBF-SVM or an RF when they are both computationally viable.
A model-agnostic practitioner may simply prefer to go with the one that provides greater accuracy.
In this light, {\em the choice of classifier can be seen as hyperparameter} alongside the $C$-value in the SVM and the max-tree-depth of the RF.
Indeed the choice and configuration of {\em pre-processing} components may likewise be seen as part of the model selection / hyperparameter optimization problem.
The Auto-Weka project \citep{thornton+hutter+hoos+leyton-brown:2013} was the first to show that an entire library of machine learning approaches (Weka~\citep{hall2009weka}) can be searched within the scope of a single run of hyperparameter tuning.
However, Weka is a GPL-licensed Java library, and was not written with scalability in mind. These factors limit the utility of Auto-Weka.
Scikit-learn~\citep{sklearn} is another library of machine learning algorithms that is written in Python with many modules in C for greater speed, and is BSD-licensed.
Scikit-learn is widely used in the scientific Python community and supports many machine learning application areas.

With this paper we introduce Hyperopt-Sklearn -- a project that brings the benefits of automatic algorithm configuration to users of Python and scikit-learn.\footnote{Project hosted at http://hyperopt.github.com/hyperopt-sklearn}
Hyperopt-Sklearn uses Hyperopt~\citep{hyperopt} to describe a search space over possible configurations of Scikit-Learn components, including pre-processing and classification modules.
Section 2 describes our configuration space of 7 classifiers and 4 preprocessing modules that encompasses a strong set of classification systems for dense and sparse feature classification (of images and text).
Section 3 presents experimental evidence that search over this space is viable, meaningful, and effective.
Section 4 presents a discussion of the results, and directions for future work.

@@

\begin{table}
  \begin{threeparttable}
    \caption{
        Hyperopt-sklearn scores (bold) relative to selections from literature on the three data sets used in our experiments.
        On MNIST, hyperopt-sklearn is one of the best-scoring methods that does not use image-specific domain knowledge (these scores and others may be found at http://yann.lecun.com/exdb/mnist/).
	On 20 Newsgroups, hyperopt-sklearn is competitive with similar approaches from the literature (scores taken from~\citet{guan2009class}).
        On Convex Shapes, hyperopt-sklearn outperforms previous automatic algorithm configuration approaches~\citep{eggensperger+etal:2013} and manual tuning~\citep{larochelle+etal:2007}.
    }
    \label{tbl:acc}
    \centering
    \small
    \begin{tabular}{llllll}
        \hline
        \multicolumn{2}{c}{\textbf{MNIST}} & \multicolumn{2}{c}{\textbf{20 Newsgroups}} & \multicolumn{2}{c}{\textbf{Convex Shapes}}  \\
        Approach & Accuracy  & Approach & F-Score & Approach & Accuracy\\
        \hline
	Committee of convnets & 99.8\%                & CFC & 0.928 & \textbf{hyperopt-sklearn} & \textbf{88.7}\%\\
	\textbf{hyperopt-sklearn} & \textbf{98.7}\%   & \textbf{hyperopt-sklearn} & \textbf{0.856} & hp-dbnet & 84.6\% \\
        libSVM grid search & 98.6\%                   & SVMTorch & 0.848 & dbn-3 & 81.4\%\\
        Boosted trees & 98.5\%                        & LibSVM & 0.843 &  &  \\
    \end{tabular}
    \begin{tablenotes}
      \footnotesize
      \item
	      \textit{In the 20 Newsgroups dataset, the score reported for hyperopt-sklearn is the weighted-average F1 score provided by sklearn. The other approaches shown here use the macro-average F1 score.} 
    \end{tablenotes}
  \end{threeparttable}
\end{table}

@@

\vspace{2em}
\noindent
{\bf Acknowledgements} \\
This research was supported by the NSERC Banting Fellowship program, the NSERC Engage program and by D-Wave Systems.
